---
title: "Riyadh Radhi LDA"
author: "Riyadh Radhi"
date: "March 3, 2019"
output:
  word_document: default
  html_document: default
---
# LDA
## Completed Task

The following report will try to construct `LDA` that will predict wheather a completed task will be **Yes** or it will be **No ** 


### 1.Step One

First, I will load all the requried libraries and set the working directory


```{r, message= FALSE, warning=FALSE}

rm(list = ls())

library(MASS)
library(dplyr)
library(ggplot2)
library(rtf)
library(scales)
library(caret)
library(class)
library(pROC)
library(ROCR)

```

### 2.Step Two

Then I will read the data and set the seed. Then I will partition my data into training and testing.

```{r}

df <- read.csv("System administrators.csv")
set.seed(175191)

index <- createDataPartition(df$Completed.task, p = 0.75,list = F)
train <- df[index,]
test <- df[-index,]

```

### 3.Step Three

Now I will make scatter plot between Training and Experience and putting the color as completed task. We can see that 
somehow we can seperate our data lineary

```{r}
ggplot(df, aes(Training, Experience))+
  geom_point(aes(col = df$Completed.task))
```


### 4.Step Four

Now I will run a discriminant analysis with both predictors using training data.


```{r}
train.lda <- lda(Completed.task ~ Training + Experience, data = train)
train.lda
```




### 5.Step Five 

After this, I will predict class labels on the test set

```{r}
pred <- predict(train.lda, newdata = test)


head(pred$class)
round(head(pred$posterior),4)
head(pred$x)
```

### 6.Step Six


Now I wil do the confusion matrix and comment on the resutls 

```{r}
confusionMatrix(test$Completed.task, pred$class)
```

Now lets explain the result of our confusion matrix. 

**Sensitivity** : Here it means that given the task was not completed what is the probability that the model will make the correct decision 

**Specificity**: Here it means that given the completed task is yes, what is the probability that the model will say so

**Positive Predictive** : True Positives/(True Positives + False Positives)
$ p = 1 / 1 $

**Negative Predictive Value** : True Negatives/(True Negatives + False Negatives)
$ p = 15/17 $

### 7 Step Seven 

Now lets find the area under the curve 

```{r}
predd <- prediction(pred$x, test$Completed.task)

perf <- performance(predd, "tpr", "fpr")

plot(perf)


performance(predd, "auc")@y.values

```


### 8 Step Eight 

Now I will take the special case of  an administrator with 4 months of experience and 6 credits of training.
Based on my results, this administrator is not going to complete the task 
```{r}
pred <- predict(train.lda, newdata = data.frame(Experience = 4,Training =6))
pred
```


